---
title: "ENormalize the greenness index"
output: NULL
author: "Jinliang Yang"
date: 03-19-2021
---

## Normalize path
```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```


# take a look at the Canopy data

1. For each plot, we have about 237 genotypes including the "check" plants.
2. For each genotype, we have multiple reps upto 8?
3. We used 9 ways to filter the data
- ExG135 to ExG140
- Otsu pre
- Otso post
- Custom
4. Additionally, in the table, we have Image id, Light.Value, Average.Saturation, 
Reference.Rep (1 indicates the reference)


### Normalize by light value and color saturation

```{r}
normcolor <- function(d=df0){
  i1 <- which(names(d) == "ExG")
  i2 <- which(names(d) == "Woebbecke..abs.")
  for(idx in i1:i2){
    d[,idx] <- d[,idx]/d$Light.Value/d$Average.Saturation
  }
  return(d)
}
df0 <- read.csv("cache/VI_average_fb2019_n46364_ref.csv")
dn <- normcolor(d=df0)
write.table(dn, "cache/VI_average_fb2019_n46364_ref_ncolor.csv", sep=",", row.names=FALSE, quote=FALSE)

```


------------------------------------

# Get Stat

```{r}
###
getstat1 <- function(df=check){

  out <- data.frame()
  nms <- names(df)
  i1 <- which(nms == "ExG")
  i2 <- which(nms == "Woebbecke..abs.")
  
  for(i in i1:i2){
    fit <- lm(df[, i] ~ Treatment + date, data=df)
    res <- summary(fit)$coefficients
    tem <- data.frame(VI=nms[i], eff=res[2,1], pval=res[2,4])
    out <- rbind(out, tem)
  }
  return(out)
}

dn <- read.csv("cache/VI_average_fb2019_n46364_ref_ncolor.csv") 
check <- subset(dn, Genotype.x %in% "Check" & Reference.Rep == 1 & Filter.Type %in% "ExG 131")

out <- getstat1(df=check)
write.table(out, "cache/pval_check_VIs.csv", sep=",", row.names = FALSE, quote=FALSE)
```


#### Plot check plants

```{r}
library(ggplot2)
library(tidyr)

d1 <- check
d1$date <- as.factor(d1$date)

i1 <- which(names(d1) %in% "ExG2")
i2 <- which(names(d1) %in% "Woebbecke..abs.")
idx <- names(d1)[c(i1:(i2-2), i2)]
df1 <- gather(d1[, c("date", "Treatment", idx)], key=VI, value=value, 3:10)

df1$date <- factor(df1$date, 
                  levels = c("July6", "Aug12", "Aug14", "Aug16", "Aug20", "Aug22", "Aug23", "Aug26", "Aug30",  "Sept1", "Sept3", "Sept5"),
                  labels =c("July 6", "Aug 12", "Aug 14", "Aug 16", "Aug 20", "Aug 22", "Aug 23", "Aug 26", "Aug 30",  "Sept 1", "Sept 3", "Sept 5"))

df1$VI <- factor(df1$VI, 
                  levels = c("ExG2", "GLI", "MGR", "NGR", "RGB", "VARI", "VEG", "Woebbecke..abs."),
                  labels = c("ExG", "GLI", "MGR", "NGR", "RGB", "VARI", "VEG", "Woebbecke"))

fsize=18
dodge <- position_dodge(width = 0.6)
p1 <- ggplot(df1, aes(x=date, y=value*1000)) +
  facet_grid(VI ~ ., scales = "free") +
  geom_violin(aes(fill = Treatment), position = dodge, trim=FALSE) + 
  geom_boxplot(aes(group = interaction(date, Treatment)), width=.1, outlier.colour=NA, position = dodge) +
  # geom_jitter(shape=16, position=position_jitter(0.2), fill=Treatment) + 
  scale_fill_manual(values=c("#E69F00", "#56B4E9"), name = "", labels = c("+N", "-N")) +
  xlab("") +
  ylab("Normalized Vegetation indices") +
  theme_classic() +
  theme(plot.title = element_text(size=20, face = "bold"), 
          axis.text=element_text(size=16, face="bold"),
          strip.text.y = element_text(size = 14, face = "bold"),
          axis.title=element_text(size=fsize-2, face="bold"),
          #axis.text.x = element_text(angle = 15, hjust=0.8),
          legend.position = "top", 
          legend.title = element_text(size=fsize-2, face="bold"),
          legend.text = element_text(size=fsize-2))
p1

```


```{r}
pdf(paste0("graphs/VIs_check.pdf"), width=12, height = 12)
p1
dev.off()
```



