---
title: "Eric data: VI Average"
output: NULL
author: "Jinliang Yang"
date: 03-03-2021
---

## Normalize path
```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```


# take a look at the Canopy data

1. For each plot, we have about 237 genotypes including the "check" plants.
2. For each genotype, we have multiple reps upto 8?
3. We used 9 ways to filter the data
- ExG135 to ExG140
- Otsu pre
- Otso post
- Custom
4. Additionally, in the table, we have Image id, Light.Value, Average.Saturation, 
Reference.Rep (1 indicates the reference)


### Exact data for different genotypes


```{r}
dn <- read.csv("cache/VI_average_fb2019_n46364_ref_ncolor.csv")
dn$date <- as.factor(dn$date)
dn$date <- factor(dn$date, 
                  levels = c("July6", "Aug12", "Aug14", "Aug16", "Aug20", "Aug22", "Aug23", "Aug26", "Aug30",  "Sept1", "Sept3", "Sept5"),
                  labels =c("July 6", "Aug 12", "Aug 14", "Aug 16", "Aug 20", "Aug 22", "Aug 23", "Aug 26", "Aug 30",  "Sept 1", "Sept 3", "Sept 5"))

dn <- subset(dn, !(Genotype.x %in% "Check"))
d1 <- subset(dn, Filter.Type %in% "ExG 131" & Reference.Rep == 1)
```


### Phenotypic data from 2019
1. Semra data
2. Yufeng leaf nutrient data

Here is the 2018 data.  The column meanings are:
 
1.      PlotID – the plot ID.  3xxx is the low nitrogen block; 4xxx is the high nitrogen block
2.      Trt – treatment. “LN” means low nitrogen, “HN” means high nitrogen
3.      DW – total dry weight of 3 sampled leaves per plant in gram
4.      CHL – average chlorophyll concentrations in 3 sampled leaves per plant in umol/m2
5.      LA – total leaf area of 3 sampled leaves per plant in cm2
6.      FW – total fresh weight of 3 sampled leaves per plant in gram
7.      N through Zn – leaf nutrient concentration in dry biomass basis in % or ppm

```{r}

### calcualte relationship between VI and leaf nutrients!
VI_leaf <- function(g1, leaf){
  ## combing VI and Leaf nutrient
  df <- merge(g1, leaf, by.x="Row", by.y="Plant.id")
  
  ### all Veg Index
  n1 <- which(names(g1) == "ExG")
  n2 <- which(names(g1) == "Woebbecke..abs.")
  VIs <- names(g1)[n1:n2]
  
  out <- data.frame()
  for(d in unique(df$date)){
    tem <- subset(df, date %in% d)
    
    if(nrow(tem) >0 ){
      # for all leaf traits
      idx1 <- which(names(tem) == "LA")
      idx2 <- which(names(tem) == "Boron")

      for(i in idx1:idx2){
        for(vi in VIs){
          test <- cor.test(tem[, vi], as.numeric(as.character(tem[,i])))
          myout <- data.frame(trait=names(tem)[i], pval=test$p.value, 
                              cor=test$estimate, type=vi, date=d)
          out <- rbind(out, myout)
        }
      }
    }
  }
  return(out)
}

### compute the relationship
leaf <- read.csv("data/pheno2019/All_data_2019 Maize Havelock.csv")
leaf <- leaf[, 1:17]

pval1 <- VI_leaf(d1, leaf)
write.table(pval1, "cache/VI_leaf_pvals_n1920_dn.csv", sep=",", row.names = FALSE, quote=FALSE)
```



Using Semra's data:

```{r}


### calcualte relationship between VI and adult phenotype!
VI_pheno <- function(g1, p){
  ## combing VI and Leaf nutrient
  df <- merge(g1, p, by.x="Row", by.y="row")
  
  ### all Veg Index
  n1 <- which(names(g1) == "ExG")
  n2 <- which(names(g1) == "Woebbecke..abs.")
  VIs <- names(g1)[n1:n2]
  
  out <- data.frame()
  for(d in unique(df$date)){
    tem <- subset(df, date %in% d)
    
    if(nrow(tem) >0 ){
      # for all leaf traits
      idx1 <- which(names(tem) == "Weight.of.20.seeds")
      idx2 <- which(names(tem) == "cob.diameter")

      for(i in idx1:idx2){
        for(vi in VIs){
          test <- cor.test(tem[, vi], as.numeric(as.character(tem[,i])))
          myout <- data.frame(trait=names(tem)[i], pval=test$p.value, 
                              cor=test$estimate, type=vi, date=d)
          out <- rbind(out, myout)
        }
      }
    }
  }
  return(out)
}

### compute the relationship
p <- read.csv("data/pheno2019/2019_yield_traits.csv")

pval2 <- VI_pheno(d1, p)
write.table(pval2, "cache/VI_pheno_pvals_n480.csv", sep=",", row.names = FALSE, quote=FALSE)

```

