---
title: "4-2 Eric data"
output: NULL
author: "Jinliang Yang"
---

## Normalize path
```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```


# take a look at the Canopy data

1. For each plot, we have about 237 genotypes including the "check" plants.
2. For each genotype, we have multiple reps upto 8?
3. We used 9 ways to filter the data
- ExG135 to ExG140
- Otsu pre
- Otso post
- Custom
4. Additionally, in the table, we have Image id, Light.Value, Average.Saturation, 
Reference.Rep (1 indicates the reference)


# Vegation Index over time

### Plot3 (-N) and Plot1 (+N)
```{r}
getwd()
```

```{r}

get_checks <- function(myptn="Plot3_canopy"){
  files <- list.files(path="largedata/Eric_Results_2-4/", pattern=myptn, full.names = TRUE)
  p1 <- read.csv(files[1], header=TRUE)
  ## understand the data structure
  # length(table(p1$Genotype))
  # [1] 237
  # subset(p1, Genotype == "NC326")


  ## cat all the data
  out <- data.frame()
  for(i in 1:length(files)){
    p <- read.csv(files[i], header=TRUE)
    p <- subset(p, Reference.Rep == 1)
    out <- rbind(out, p)
  }
  out$date <- gsub("_.*", "", out$Filename)
  g1 <- subset(out, Genotype == "check")
  return(g1)
}

df1 <- get_checks(myptn="Plot1_average")
df1$Nitrogen <- "+N"
df2 <- get_checks(myptn="Plot3_average")
df2$Nitrogen <- "-N"
g1 <- rbind(df1, df2)


library(ggplot2)
library(plyr)

g2 <- subset(g1, date != "190706")
df <- ddply(g2, .(date, Filter.Type, Nitrogen), summarise,
            m= mean(VARI, na.rm=TRUE),
            sd=sd(VARI, na.rm=TRUE))

df <- subset(df, Filter.Type %in% c("Custom", "ExG 135", "ExG 140", "Otsu post"))
df$Filter.Type <- gsub("Otsu post", "Otsu", df$Filter.Type)

fsize=18
p3 <- ggplot(data = df, aes(x = date, y = m  )) +
      geom_line(group=1, size=2, aes(color = Filter.Type)) +
      geom_point()+
      geom_errorbar(aes(ymin=m-sd, ymax=m+sd), width=.2,
                 position=position_dodge(0.05)) +
      labs(title="", x="Dates", y = "VARI")+
      theme_classic() +
      # scale_color_manual(values=c('#999999','#E69F00'))
      facet_grid(Filter.Type ~ Nitrogen) +
      theme(axis.title=element_text(size=fsize, face="bold"),
                legend.title = element_text(size=fsize, face="bold"),
                legend.text = element_text(size=fsize),
            axis.text.x = element_text(face="bold", color="#993333", 
                           size=20, angle=45),
            axis.text.y = element_text(face="bold",
                           size=14),
            strip.text = element_text(size = fsize))

p3

```

```{r}
# ExG       RGB        NGR
# GLI       MGR      VARI      VEG Woebbecke..no.abs. Woebbecke..abs
df <- ddply(g2, .(date, Filter.Type, Nitrogen), summarise,
            m= mean(ExG),
            sd=sd(ExG))

fsize=18
p3 <- ggplot(data = df, aes(x = date, y = m  )) +
      geom_line(group=1, size=2, aes(color = Filter.Type)) +
      geom_point()+
      geom_errorbar(aes(ymin=m-sd, ymax=m+sd), width=.2,
                 position=position_dodge(0.05)) +
      labs(title="", x="Dates", y = "ExG")+
      theme_classic() +
      # scale_color_manual(values=c('#999999','#E69F00'))
      facet_grid(Filter.Type ~ Nitrogen) +
      theme(axis.title=element_text(size=fsize, face="bold"),
                legend.title = element_text(size=fsize, face="bold"),
                legend.text = element_text(size=fsize),
            axis.text.x = element_text(face="bold", color="#993333", 
                           size=20, angle=45),
            axis.text.y = element_text(face="bold",
                           size=14),
            strip.text = element_text(size = fsize))

p3

```

```{r}
# ExG       RGB        NGR
# GLI       MGR      VARI      VEG Woebbecke..no.abs. Woebbecke..abs
df <- ddply(g2, .(date, Filter.Type, Nitrogen), summarise,
            m= mean(Woebbecke..abs.),
            sd=sd(Woebbecke..abs.))

fsize=18
p3 <- ggplot(data = df, aes(x = date, y = m  )) +
      geom_line(group=1, size=2, aes(color = Filter.Type)) +
      geom_point()+
      geom_errorbar(aes(ymin=m-sd, ymax=m+sd), width=.2,
                 position=position_dodge(0.05)) +
      labs(title="", x="Dates", y = "Woebbecke (abs)")+
      theme_classic() +
      # scale_color_manual(values=c('#999999','#E69F00'))
      facet_grid(Filter.Type ~ Nitrogen) +
      theme(axis.title=element_text(size=fsize, face="bold"),
                legend.title = element_text(size=fsize, face="bold"),
                legend.text = element_text(size=fsize),
            axis.text.x = element_text(face="bold", color="#993333", 
                           size=20, angle=45),
            axis.text.y = element_text(face="bold",
                           size=14),
            strip.text = element_text(size = fsize))

p3

```

```{r}
# ExG       RGB        NGR
# GLI       MGR      VARI      VEG Woebbecke..no.abs. Woebbecke..abs
df <- ddply(g2, .(date, Filter.Type, Nitrogen), summarise,
            m= mean(MGR),
            sd=sd(MGR))

fsize=18
p3 <- ggplot(data = df, aes(x = date, y = m  )) +
      geom_line(group=1, size=2, aes(color = Filter.Type)) +
      geom_point()+
      geom_errorbar(aes(ymin=m-sd, ymax=m+sd), width=.2,
                 position=position_dodge(0.05)) +
      labs(title="", x="Dates", y = "MGR")+
      theme_classic() +
      # scale_color_manual(values=c('#999999','#E69F00'))
      facet_grid(Filter.Type ~ Nitrogen) +
      theme(axis.title=element_text(size=fsize, face="bold"),
                legend.title = element_text(size=fsize, face="bold"),
                legend.text = element_text(size=fsize),
            axis.text.x = element_text(face="bold", color="#993333", 
                           size=20, angle=45),
            axis.text.y = element_text(face="bold",
                           size=14),
            strip.text = element_text(size = fsize))

p3

```